Value-Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-25 paper/paper.tex
Heuristics in text
Hail Santa!
Put words back in

        \nl \tikzmark{restart1s}$\KwSty{global}~(R, R') \gets (0,\,\textnormal{the next Luby value})$\tikzmark{restart1e} \;

@@

    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \siplabel{pickd} \;

@@

    \nl \ForEach {$v' \in D_v~\textnormal{ordered by chosen heuristic}$\siplabel{parforeach}}{

@@

these, partly because some earlier solvers find many of these instances extremely hard, and partly
to avoid skewing a portfolio. We want larger numbers of satisfiable instances, so we include all
pattern / target pairs.

>>>>

        \nl \tikzmark{restart1s}$\KwSty{global}~(R, R') \gets (0, 666 \times \textnormal{the next Luby value})$\tikzmark{restart1e} \;

@@

    \nl $D_v \gets \textnormal{a domain from}~D~\textnormal{chosen by variable heuristic}$ \siplabel{pickd} \;

@@

    \nl \ForEach {$v' \in D_v~\textnormal{ordered by chosen value heuristic}$\siplabel{parforeach}}{

@@

?? Other studies use a random selection of 200 of the mesh instances, partly because some earlier
solvers find many of these instances extremely hard, and partly to avoid skewing a portfolio. We
want larger numbers of satisfiable instances, so we include all pattern / target pairs.
